My title

### 2024-02-15 outputs/paper/paper.qmd
add features

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}
```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
bully_clean_data$date <- as.Date(bully_clean_data$date)
pop_2019_clean<- read.csv("../../outputs/data/pop_2019_clean.csv")
pop_2020_clean<- read.csv("../../outputs/data/pop_2020_clean.csv")
state_ratios<- read.csv("../../outputs/data/state_ratios.csv")
sample_data <- head(bully_clean_data, 6)
```

@@

It is clear that the incidence of school bullying has generally been decreasing over time. The original paper [cite] states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases. Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity). It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020. The unexpected rise in bullying during the pandemic could be attributed to various factors, for example, individuals seeking to alleviate stress through harmful behavior to other people. Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus [@citeChineseHate]. Asian students, especially Chinese ethnicity, might experience discriminatory actions, verbal abuse, or physical assaults due to this misinformation. So it most likely contributed to an increase in school bullying cases. As schools closed down in February 2020, a consequential decline in bullying cases was observed, at times nearly reaching zero. This is understandable since student interactions have declined due to remote learning.

>>>>

# Introduction
With pandemic outbreaks, most schools in the United States turned to online teaching models, and students moved from physical places with more social interaction to screens [@citeCovid19Effect]. While the transition to virtual education has been accompanied by a variety of challenges, including academic setbacks and economic disparities, significant gaps remain in understanding the impact of virtual education on the social dynamics within schools. Most research has focused on education, i.e., whether this change to an online delivery model will affect student achievement. In this article, we will focus on a new aspect of the pandemic that is having a positive impact: school bullying.

Bullying in schools is pervasive and can have significant social costs. In the US, 1 in 5 students ages 12-18 has been bullied during the school year, and approximately 160,000 teens have skipped school because of bullying [@citeFacts]. The COVID-19 pandemic has fundamentally changed the context of bullying dynamics. With the shift to online learning across the United States in March 2020, there is a sudden decrease in in-person communication and interaction while the use of technology increases dramatically. In fact, prior COVID-19 research has suggested that the higher the frequency of the Internet, the more incidents of cyberbullying and cyber-victimization reported by youth [@citeResearch]. However, in this paper, we conclude that both school bullying and cyberbullying have been decreased during the pandemic by analyzing a long panel of publicly available Google Trends online search data. These results provide insights into how schools can reduce bullying in a post-pandemic world and highlight a possible mechanism by which COVID-19 may have a differential impact on broader mental health.

# Data {#sec-data}

## Data Source
This paper will replicate the data that was originally collected for the paper “The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying” by [citation]. Using the online platform “Google Trends”, which provide monthly internet search behavior for a given term or topic by states over a period of time, they collected three types of bullying data (“School Bullying”, “Cyberbullying”, and “Bullying”) before, during, and after the pandemic COVID-19 from January 2012 to February 2021. They filtered the data to keep male and female individuals between ages of 5 and 17 (roughly the k-12 schooling population). Each dataset contains 5661 rows and 5 variables, each indicating a detailed summary of the month and position of the search, search keyword, number of searches and the ratio.

The researchers state that data from Google Trends are less likely to be subjected to potential bias, since the data are not self-reported. Moreover, the data from Google Trends represents the full population of Google search users in the United States, thus it does not have the potential issue of under-representation of a certain group.

## Methodology
Since it is difficult to observe through 16683 (5661*3) rows with 5 variables, this report will only observe and analyze through specific aspects. The original dataset contains information through all the 51 states in the US. This paper focuses only on data and trends for three states, which are “US-LA”, “US-NY” and “US-NJ” (Louisiana, New York, and New Jersey respectively).
Some data cleaning is performed, such as renaming column names, filtering and mutating the column, etc. The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `knitr` (@citeKnitr), `dplyr` (@citeDplyr), `ggplot2` (@citeGgplot2).

## Features
The original dataset contained 5 variables, which are named as “dma_json_code”, “date”, “keyword”, “hits”, and “ratio”. 
1. dma_json_code: the states of the United States
2. date: the first day of every month from 2012. 01 to 2021. 02
3. keyword: specific words that the people search on Google Trends that relate to bullying.
4. hits: number of searchers of keywords in each month.
5. ratio:

```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
bully_clean_data$date <- as.Date(bully_clean_data$date)
pop_2019_clean<- read.csv("../../outputs/data/pop_2019_clean.csv")
pop_2020_clean<- read.csv("../../outputs/data/pop_2020_clean.csv")
state_ratios<- read.csv("../../outputs/data/state_ratios.csv")
sample_data <- head(bully_clean_data, 6)
```

@@

It is clear that the incidence of school bullying has generally been decreasing over time. The original paper [cite] states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases. Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity). It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020. The unexpected rise in bullying during the pandemic could be attributed to various factors, for example, individuals seeking to alleviate stress through harmful behavior to other people. Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus [@citeChineseHate]. Asian students, especially Chinese ethnicity, might experience discriminatory actions, verbal abuse, or physical assaults due to this misinformation. So it most likely contributed to an increase in school bullying cases. As schools closed down in February 2020, a consequential decline in bullying cases was observed, at times nearly reaching zero. This is understandable since student interactions have declined due to remote learning. They did not have  as much opportunity or motivation to bully others as they had before.
